---
title: "Apriori Analysis for TCM"
author: "Xianying, Tan"
date: "2016年3月2日"
output: html_document
---

## The packages that are needed 
_(You'll not be able to exec the script without installing the following packages)_

### For data mungling:
- dplyr
- ggplot2
- readr
- purrr
- stringr # character manipulation
- showtext # show Chinese in the plot

### For data mining:
- arules
- arulesViz


## Setting up the environment

```{r setting, echo=TRUE, message=FALSE, warning=FALSE}
showtext::showtext.auto()
library(dplyr)
library(ggplot2)
library(arules)
library(arulesViz)
```

## Reference

- [R语言与关联分析（转载）](http://blog.sina.com.cn/s/blog_6aed37fd0101qe27.html)

## Read data & have a glimpse

Read the data from the csv file and assign it to `r` variable.

```{r}
d <- readr::read_csv("data.csv", locale = readr::locale(encoding = "GB2312"), col_names = FALSE)
tmp <- purrr::flatten_chr(d)
tmp <- table(tmp)
tmp <- sort(tmp, decreasing = TRUE)
head(data_frame(Item = names(tmp), Count = unname(tmp)), 20)
plot(tmp)
```

## Data Analysis

### Data preparing

i.e., convert the character matrix (in fact it's been storaged in a `data_frame` for now) to `transaction-class`, so that we can use `arules` to continue the analysis.

```{r}
r <- as.data.frame(t(d))
r <- lapply(r, stringr::str_trim, side = "both") # remove the space of the text
r <- lapply(r, unique) # ensure each case's desc is unique
r <- lapply(r, function(x) {
  x[stringr::str_length(x) == 0] <- NA_character_
  x
})
names(r) <- paste0("Case-", 1:length(r))
r <- as(r, "transactions")
```

### Do the sampe analysis as in the _Reference_

```{r, fig.width=12, warning=FALSE, dev='svglite'}
rules <- apriori(r, parameter = list(support = 0.01, confidence = 0.2))

inspect(sort(rules, by = "support")[1:6]) #按支持度查看前6条规则
inspect(sort(rules, by = "confidence")[1:6]) #按置信度查看前6条规则
inspect(sort(rules, by = "confidence")[1:6])
# sub.rules=subset(rules, subset = rhs %in% "whole milk" &lift > 1.2) #也可以用subset做规则的筛选,取"右手边"含有whole milk且lift大于1.2的规则

itemFrequencyPlot(r, support = 0.05, cex.names = 0.8) #数据画频繁项的图

# plot(rules, shading = "order", control = list(main = "Two-key plot"))#见chart.1
# plot(rules, method = "grouped")#见chart.2
# plot(rules, method = "graph")#见chart.3
```


